I want to thank my collaborators and advisors. Jason Moore, who introduced me to research back in 2011, taking a chance on a high school student with no prior research experience. Peter Andrews, who mentored me and was always tuned into the next potential developments. Chris Bailey-Kellogg and Yoonjoo Choi, who taught me about computational structural biology, and especially immunology -- who would have known how relevant that knowledge would become for day-to-day life? Sean Smith who introduced me to security research; I still do not know what could possibly replace passwords. Mona Singh, who helped guide me in my first few months of graduate school. Nick Feamster, who introduced me to web measurement studies; though I didn't know it at the time, that would eventually become the focus of this dissertation. Ed Felten, who taught me about cryptography and has advised me for years. Mark Zhandry, who showed me the quantum angle to cryptography. Prateek Mittal, who has closely advised me, especially throughout the pandemic; without Prateek's guidance I would not have been able to complete this dissertation. Gunes Acar, Arvind Narayanan, Mihir Kshisagar, and Jonathan Mayer for guiding me through the tricky world of privacy policies. Joe Calandrino, who showed me the exciting opportunities for impact in the government and helped me realize this dissertation. Sam Ginzberg, who brought me onboard a project which turned out to be the perfect opportunity to learn information theory. Eli Lucherini, who pulled together a powerful classifier after an impressive amount of manual labelling. And Roland Maio, who introduced me to game theory and helped me navigate the weird world of online reviews.

I want to thank my friends and family. \raNote{enumerate}.
Friends and family
Siddharth Desai
Lucina Schwartz
Jordan Dull
Andrew Shapiro
Chris Phenicie
Julie LaChance
Al Gaillard
Chaitanya Aluru
Thomas Schaffner
Luc Desroaches

Lucina Schwartz

Mom, Dad, Brendan

I want to provide specific credit to my collaborators who directly contributed to the research and text in this work. Mihir Kshisagar wrote most of Section \ref{sec:ppot:background}. Jonathan Mayer wrote most of Section \ref{sec:ppot:related}. Gunes Acar scaled up the longitudinal data collection and wrote much of Section \ref{sec:ppot:dataset} and part of Section \ref{sec:ppot:policy-updates}. Eli Lucherini developed the classifier for and wrote Section \ref{sec:ppot:classifier}. Gunes Acar, Eli Lucherini, Mihir Kshisagar, Arvind Narayanan, and Jonathan Mayer all provided feedback on and helped edit the paper from which Chapter \ref{ch:ppot} derives. Roland Maio, Joe Calandrino, and Prateek Mittal all provided feedback on and helped edit the paper from which Chapter \ref{ch:rim} derives. This dissertation would not be where it is without the input of my advisor Prateek Mittal and my readers, Joe Calandrino and Jonathan Mayer.
%Specific credit to collaborators who directly contributed to text of this dissertation