\section{Conclusion}
\label{sec:conclusion}
We developed a system for the longitudinal, large-scale, automated collection and curation of privacy policies. Using the system we built a dataset of over 1M privacy policies that span more than two decades. We found that privacy policies are becoming longer and harder to read.

We developed an automated trend surfacing tool and investigated some of the surfaced trends. Specifically, we investigated trends around third parties, tracking technologies, and self-regulatory bodies. Our results suggest that privacy policies show a concerning lack of transparency: the usage of third parties and tracking technologies is severely underreported.

Our results add to the growing body of evidence suggesting the inadequacy of the ``notice and choice'' model for privacy policy regulation and demonstrate the monumental impact of the GDPR.


\input{sections/data-code-release}

\input{sections/limitations}

\textbf{Future work.}
Based on our results we suggest several directions for future work. The reporting gap for third parties and tracking technologies could be investigated with a combination of web measurements and privacy policy analysis. Another direction is to further investigate ambiguity in privacy policies.

More sophisticated natural language processing techniques applied to longitudinal privacy policy data could improve our understanding of how online services adapt to new privacy regulations, the prevalence of specific business practices, and whether online services are complying with privacy laws. 
We anticipate that our dataset will prove useful for research in all of these directions.
