\subsection{Cleaning the corpus}
\label{sec:deduplication}
In order to ensure the quality of our analysis, we purged additional, real policies from our dataset that might lead to a biased analysis. In total, we removed 160,941 policies following the steps listed below, leaving us with 910,546 policies from 108,499 sites. We call the resulting corpus the \textit{analysis subcorpus}. In sections \ref{sec:dataset}, \ref{sec:doclevstatstime}, and \ref{sec:analysis} we use the analysis subcorpus for our analyses.\footnote{While we removed this data for our analyses, we anticipate that there may be some research questions that would benefit from their inclusion. Accordingly, in our public release, we include both the full corpus and the analysis subcorpus.} 

\textbf{Parked domains.} As our dataset spans more than 20 years,
many domains have expired and were parked for monetization.
We found that privacy policies of the parking services such as {\tt godaddy.com} and {\tt hugedomains.com} were abundant in our dataset as they hosted privacy policies of 7,092 and 2,275 distinct domains, respectively.
We built a detection method based on the lists of domain parking services and registrars from prior research~\cite{vissers2015parking, kuhrer2014paint, kuhrer2014paint-TR, wang2006strider},
and the ICANN-Accredited Registrars list~\cite{ICANN-Registrars}.
With this method, we detected 79 parking providers and resellers and removed 24,289 (2.3\%) snapshots hosted by these providers.
 
\textbf{Homepage redirection.} In order to ensure the metadata is consistent with policy content, we removed policy snapshots with a cross-origin homepage redirection (COHR), unless both sites were likely owned by the same entity. Thus, we removed COHR policy snapshots, but we made an exception for websites with
common~\emph{label}s in their domain names (e.g. \texttt{google.com} and \texttt{google.ca})
as this may indicate that they are owned by the same organization.

\textbf{Policy URL.} Finally, to remove duplicates, we followed
Degeling et al.'s approach based on privacy policy URLs~\cite{degeling2018we}. When two or more sites shared a policy URL during the same interval, we kept only one, preferring the snapshot where the homepage domain matched the privacy policy domain. This removed 61,220 policies.



